---
title: "Displaying Multiple Charts in RMarkdown"
subtitle: How to create a drop down menu that users can pick charts from
date: "`r format(Sys.time(), '%d %B %Y (%H:%M:%S)')`"
output:
  html_document:
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This takes the example from here https://walkerke.github.io/2016/12/rmd-dropdowns/ and creates a working example using other open data that you can more easily adapt.

First we install the package with devtools as it's not on CRAN

```{r echo=TRUE, message=FALSE, warning=FALSE}
# devtools::install_github("walkerke/bsselectR")
```

# Generate multiple plot PNG files

Then we generate multiple plots using the excellent functional programming with plotting example here: https://b-rodrigues.github.io/modern_R/functional-programming.html#functional-programming-and-plotting

```{r echo=TRUE, message=FALSE, warning=FALSE,results="hide"}
library(bsselectR)
library(tidyverse)
library(RCurl)
url_csv <- RCurl::getURL("https://raw.githubusercontent.com/b-rodrigues/modern_R/master/datasets/unemployment/all/unemployment_lux_all.csv")

unemp_lux_data <- read.csv(text = url_csv) %>%
  dplyr::filter(division %in% c('Beaufort','Bech','Berdorf'))

plots_tibble = unemp_lux_data %>%
  dplyr::group_by(division) %>%
  tidyr::nest() %>%
  dplyr::mutate(plot = purrr::map2(.x = data, .y = division, ~ggplot2::ggplot(data = .x) +
       ggplot2::theme_minimal() +
       ggplot2::geom_line(aes(year, unemployment_rate_in_percent, group = 1)) +
       ggplot2::labs(title = paste("Unemployment in", .y))))

purrr::map2(paste0(plots_tibble$division, ".png"), plots_tibble$plot, ggplot2::ggsave,path = "plots", dpi = 300)
```

# Use bselectR to display plots with drop down

```{r echo=TRUE, message=FALSE, warning=FALSE}
division_plots <- paste0(list.files("plots", full.names = TRUE))

names(division_plots) <- str_replace_all(division_plots, 
                                      c("\\.png" = "", 
                                        "plots/" = ""))

bsselect(division_plots, type = "img", selected = "Beaufort", 
         live_search = TRUE, show_tick = TRUE)
```

# Use plotly to display plots with drop down


```{r echo=TRUE, message=FALSE, warning=FALSE, eval = FALSE}
plotly::plot_ly(data = unemp_lux_data,x=~year, y= ~unemployed, color = ~division, mode = 'lines') %>%
  layout(
    updatemenus = list(
      list(
        yanchor = 'auto',
        buttons = list(
          
          list(method = "restyle",
               args = list("visible", list(T,T,T)),
               label = 'All of them'),
          
          list(method = "restyle",
               args = list("visible", list(T, F,F)),
               label = 'Beaufort'),
          
          list(method = "restyle",
               args = list("visible", list(F,T,F)),
               label = 'Bech'),
          
          list(method = "restyle",
               args = list("visible", list(F,F,T)),
               label = 'Berdorf')
        ))))

```

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(plotly)
plot_ly(mtcars, x = rownames(mtcars), y = ~mpg, name='mpg', type='scatter', mode='markers') %>%
  add_trace(y = ~hp, name = 'power', type='scatter', mode='markers') %>%
  add_trace(y = ~qsec, name = 'qsec', type='scatter', mode='markers') %>%
  layout(
    updatemenus = list(
       
      list(
        type = "buttons",
        x = -0.1,
        y = 0.7,
        label = 'Category',
        buttons = list(
          list(method = "restyle",
               args = list('visible', c(TRUE, FALSE, FALSE)),
               label = "mpg"),
          list(method = "restyle",
               args = list('visible', c(FALSE, TRUE, FALSE)),
               label = "hp"),
          list(method = "restyle",
               args = list('visible', c(FALSE, FALSE, TRUE)),
               label = "qsec")
        )
      )
    )
  )
```

